surfing

### 2021-08-10 inst/surfing.Rmd
typo

```{r directlogplotofstrenghts}
jjO <- surfing_table$points[wanted]
names(jjO) <- rownames(surfing_table)[wanted]
jjL <- surfing_maxp
jjO <- ordertrans(jjO)
jjL <- ordertrans(jjL)
plot(jjO,jjL,pch=16,log='xy')
fit <- lm(log10(jjL)~log10(jjO))
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.5)
}
abline(fit)
```

>>>>

```{r directlogplotofstrengths,cache=TRUE}
jjO <- surfing_table$points[wanted]
names(jjO) <- rownames(surfing_table)[wanted]
jjL <- surfing_maxp
jjO <- ordertrans(jjO)
jjL <- ordertrans(jjL)
plot(jjO,jjL,pch=16,log='xy',xlab='points',ylab='maximum likelihood strength')
fit <- lm(log10(jjL)~log10(jjO))
summary(fit)
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.5)
}
abline(fit)
```
